\documentclass{article}

\usepackage{lmodern}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[top=1.7cm, bottom=1.7cm, left=1.7cm, right=1.7cm]{geometry}
\usepackage{verbatim}
\usepackage{tikz} %Vectoriel
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{multido}
\usepackage{amssymb}

\newcommand{\titre}{Uranium could be the future of hard drives}

\newcommand{\module}{}
\newcommand{\sigle}{lan}

\newcommand{\semestre}{3}

\input{/home/satenske/cours/listings.tex} %prise en charge du langage algo
\title{\titre}
\date{Antoine de \textsc{Roquemaurel}
Group B\newline \newline \today
}

\lhead{\titre}
\chead{Antoine de Roquemaurel}
\rhead{\thepage}

\lfoot{Université Paul Sabatier Toulouse III}
\cfoot{\thepage}
\rfoot{\sigle\semestre}

\pagestyle{fancy}

\begin{document}
\maketitle
\paragraph{}
	since the beginning of computer, computer needs hard disk drive, the capacity in which computers need increases steadily.\\
	So the hard drives actually, it's several discs with aluminium and a magnetic field on this disc. If the number of disks increases,
	the storage capacity increases!
	\paragraph{}
	The depleted uranium, the same material that the military uses, may one day be used for super-high density storage in hard drives.
	The uranium must be preserved in cold temperature, in $2^{\circ}K$ whether $-271.16^{\circ}C$. \\
	So a researcher found a molecule who the magnetic field is big. If we build hard drives with this molecule, we can have hard disk drive
	who the capacity is 1000 times more important. 
	\paragraph{}
	If we arrive to have hard disk drive with uranium, we can use in server, than Google, Facebook, Microsoft, \ldots or they can use on supercomputer for example. \\
	In fact this hard disk can be faster than old, and actually, server use many hard drive different with RAID, if they have
	two big disk (one disk use to backup), they must be faster to the write and read on the hard disks. \\
	However, the hard disk to uranium will never be used in individuals.  \\
	There is an other inconvenient, the uranium is bad to ecology, so we don't want to have radioactive in our computer. 
	\paragraph{}
	So, this discovery can not be use on industry, in fact it's actually impossible to have a temperature of $2^{\circ}K$, we don't arrive to have
	atoms close to the immobility.\\
	However, that shows that researcher looking for new storage methods, and we are moving forward in technology, in several years we may be
	have big hard disk drives! 



\end{document}

