\documentclass[a4paper, 11pt]{book}

\usepackage{lmodern}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english, francais]{babel}
\usepackage[top=1.7cm, bottom=1.7cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{verbatim}
\usepackage{tikz} %Vectoriel
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage{multido}
\usepackage{amssymb}

\newcommand{\titre}{Subject 4}
\newcommand{\typeDoc}{Essay}

\newcommand{\module}{English}
\newcommand{\sigle}{english}

\newcommand{\semestre}{3}

\input{/home/satenske/cours/includesLaTeX/listings.tex} %prise en charge du langage algo
\input{/home/satenske/cours/includesLaTeX/l2/tddm.tex}

% Benefit 
%	=> Learn foreign language
%	=> You live in and learn about another culture
%	=> You become more independent
%	=> you benefit from other approaches to studying
%	=> Good experiment

% Bad 
%	=> Very difficult
%		=> You must understand the lecture
%		=> You are alone
%
%
%

\begin{document}
	\selectlanguage{english}
	\maketitle
	\subsection*{Do you think your education would benefit from a year at a foreign university~?}
		In France, go to a foreign university is common in an enginneering school. On account of the many benefit of the foreign studies.\\

		As I see it, there is a few inconveniences and many benefits. In fact, study in a foreign language is very difficult, I must understand the lecture, take notes, so I will work harder than people of this country. 

		In addition, I will be alone, in a foreign country, it can be difficult to start, and I could have homesick. \\

		On the other hand, there is many benefits of the foreign studies. Firstly, I could learn the language of the country, it will be difficult at beginning (the first weeks), but it was benefit.

		Secondly, I will see other approaches to studying, it's very interesting to know the educational system of another country. In this connection, if I do in another country, I should have a correspondence in the studies. So if I would go in European country, there is the LMD system to encourage the foreign studies.

		Lastly, I would have an very good experiment, that I could put on the CV.\\

	To conclude, my education would benefit if I go in a foreign university, I think the abroad programme could be an ``life-changing'' experience.



\end{document}





